Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-21 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
More AUDPC

# Pick up from here

```{r}
# Columns to keep
Fogerty_17 <- Fogerty_17[, c('Plot', 'Rep', 'Row', 'Column', 'Chem.Trt',
                           'Chemical', 'Row.Spacing.(m)', 'Treatment.No',
                           'Treatment', 'Population.plsnts/ha',
                           '2017-03-07', '2017-03-19', '2017-03-24',
                           '2017-04-02', '2017-04-10', '2017-04-18',
                           'Yield.t/ha', 'Grain.Moisture.%', 'Temp.moisture.Taken',
                           '100.grain.wt.Grams')]

# Create summarised data set for collated means meta-dataset
# NEXT STEP - sort and copy it to dataset
Herm_17_sum <- Herm_17 %>%
   group_by(Chemical,
            Chemical.Trt,
            `Row.Spacing.(m)`,
            Manage.Trt,
            Management) %>%
   summarise(
      PM_final_severity = mean(`I_11/05/2017`, na.rm = TRUE),
      Disease_error = sd(`I_11/05/2017`, na.rm = TRUE),
      `grain_yield(t/ha)` = mean(`Yield.T/Ha`, na.rm = TRUE),
      Yield_error = sd(`Yield.T/Ha`, na.rm = TRUE),
      meanSq = anova(lm(`Yield.T/Ha` ~ factor(Manage.Trt) + factor(Trt) + `Row.Spacing.(m)`, data = subset(Herm_17, Chemical != "Custodia® 320 SC")))[1,3] # of only triazoles
   )

Herm_17_sum <-
   with(Herm_17_sum, Herm_17_sum[order(Manage.Trt, Chemical, `Row.Spacing.(m)`), ])

# inserted meansquare in manually

# Columns to keep
Herm_17 <- Herm_17[, c(1, 2, 4, 5, 7, 10, 9, 11, 12, 13,
                       17, 19, 21, 23, 25, 27, 29,
                       #                      18,20,22,24,26,28,30,
                       34, 36, 37, 35)]

@@

>>>>

#### Calculating treatment means
```{r Herm17_means}

Herm_17_m <- Herm_17_dat %>%
   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = anova(lm(grain_yield.t.ha. ~ 
                                  factor(n_treatment) + fungicide_ai + row_spacing, 
                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )
sd(Herm_17_dat$PM_final_severity)

# For some weird reason standard deviations are comming back NA in the code above
Herm_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
   Herm_17_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

write.csv(
   Herm_17_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2017/Hermitage/Hermitage_17_mean.csv",
   row.names = FALSE
)

@@

# Start from here
